---
title: "MA677 Assignment"
author: "Zhitian Liu"
output:
  html_document:
    df_print: paged
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse","Hmisc")
```





## Fiji earthquakes
Data on the magnitudes of earthquakes near Fiji are on Blackboard under the Class-21
tab. Estimate the cdf F(x). Compute and plot a 95% confidence envelope for F. Find an
approximate 95 percent confidence interval for F(4.9) − F(4.3).

```{r}
fiji=read.csv("C:/Users/Lenovo/Desktop/fijiquakes.csv")
#The CDF of magnitude
CDF<-ecdf(fiji$mag) 
plot(CDF)
#  95% confidence envelope for F
alpha <- 0.05
n <- length(fiji$mag)
epsn<-sqrt(log(2/alpha)/(2*n))
r<-max(fiji$mag)-min(fiji$mag)
grid<-seq(from=min(fiji$mag),to=max(fiji$mag),l=1000)
low.cdf<-pmax(CDF(grid)-epsn,0)
up.cdf<-pmin(CDF(grid)+epsn,1)
lines(grid,low.cdf,col="blue",lty=2)
lines(grid,up.cdf,col="red",,lty=2)


# use wilson method to calculate the confidence interval for F(4.9) − F(4.3)
a=ifelse((fiji$mag<=4.9) & (fiji$mag>4.3),1,0)
num_intherange<-sum(a)
binconf(num_intherange,length(fiji$mag),method="wilson",alpha)
#Hence the 95% confidence interval for F(4.9) − F(4.3) would be (0.495,0.557)
```

## Old Faithful

Data on eruption times and waiting times between eruptions of the old faithful geyser
(located in Yellowstone National Park) are posted on Blackboard under the Class-21 tab.
Estimate the mean waiting time and compute a standard error for the estimate. Also,
calculate a 90 percent confidence interval for the mean waiting time. Finally, estimate the
median waiting time. We will use this calculation of the median in our discussions next
week.

```{r}
geysers=read.csv("C:/Users/Lenovo/Desktop/geysers.csv")
CDF=ecdf(geysers$waiting)
plot(CDF)
wt=geysers$waiting
#mean waiting time
mean_wt=mean(wt)
#standard error of the estimate
SEM=sd(wt)/sqrt(length(wt))
#90 percent confidence interval for the mean waiting time
low=mean_wt-qnorm(0.95)*SEM
up=mean_wt+qnorm(0.95)*SEM
#the median waiting time
mid=median(wt)
#print
paste("the mean of the waiting time is ",mean_wt )
paste("the standard error of the estimate waiting time is ",SEM )
paste("the median of the waiting time is ",mid )
paste("the 90 percent confidence interval for the mean waiting time is from",low,"to",up)
```

## KS problem
Use the Kolmogorov-Smirnov test to test the hypothesis that the 25 values in the table below
form a random sample from the uniform distribution on the interval [0, 1].
0.42 0.06 0.88 0.40 0.90
0.38 0.78 0.71 0.57 0.66
0.48 0.35 0.16 0.22 0.08
0.11 0.29 0.79 0.75 0.82
0.30 0.23 0.01 0.41 0.09
Using the table above, test the hypothesis that the 25 values are a random sample from a
continuous distribution with pdf:......

```{r}
x=c(0.42,0.06,0.88,0.40,0.90,
0.38,0.78,0.71,0.57,0.66,
0.48,0.35,0.16,0.22,0.08,
0.11,0.29,0.79,0.75,0.82,
0.30,0.23,0.01,0.41,0.09)
ks.test(x,punif)


```
Since the p-value of the One-sample Kolmogorov-Smirnov test is 0.35, we accept the null hypothesis, The sample is drawn from uniform distribution.

```{r}
x=c(0.42,0.06,0.88,0.40,0.90,
0.38,0.78,0.71,0.57,0.66,
0.48,0.35,0.16,0.22,0.08,
0.11,0.29,0.79,0.75,0.82,
0.30,0.23,0.01,0.41,0.09)
#CDF of the given distribution
p=function(x){
  if(x<=0.5&x>=0) {
    1.5
  } else if (0.5<x&x<1 ) {
   0.5+0.5*x
  } else {
   0
  }
}
ks.test(x,p)
```
Since the p-value of the One-sample Kolmogorov-Smirnov test is small enough, we reject the null hypothesis, The sample isn't drawn from the given distribution.

## Exercises 8.5.2

Let $X_1,X_2,X3....X_n~Bernoulli(p)$ and let $Y_1,Y_2,Y3....Y_n~Bernoulli(q)$. Find the plug-in estimator and estimated standard error for p. Find an approximate 90 percent confidence interval for p. Find the plug-in estimator and estimated standard error for p-q. Find an approximate 90 per cent confidence interval for p-q.

Answer:
The plug in estimator For p is $\hat p= \overline X_n$. The plug in estimator for standard error of Bernoulli(p) is $\sqrt{\hat p(1-\hat p)}=\sqrt{ \overline X_n(1- \overline X_n)}$.

approximate 90 percent confidence interval for p is $$\hat p+-z\hat {se}=\overline X_n+-z\sqrt{ \overline X_n(1- \overline X_n)} $$

The plug in estimator for p-q is $\hat \theta=\hat p-\hat q=\overline X_n-\overline Y_n$. The plug in estimator for standard error of p-q is 
$se=\sqrt{V(\hat p-\hat q)}=\sqrt{V(\hat p)+V(\hat q})=\sqrt{ (\overline X_n(1- \overline X_n))^2+\overline (Y_n(1- \overline Y_n))^2}$

approximate 90 per cent confidence interval for p-q is
$$\overline X_n-\overline Y_n+-z\sqrt{ (\overline X_n(1- \overline X_n))^2+\overline (Y_n(1- \overline Y_n))^2}$$

## Exercises 8.5.4
Let $x$ and $y$ be two distinct points. Find $Cov(\hat{F_n}(x),\hat{F_n}(y))$

Answer:
$$
\begin{align}
\\Cov(\hat{F_n}(x),\hat{F_n}(y)) & = E(\hat{F_n}(x) \hat{F_n}(y)) - E(\hat{F_n}(x))E(\hat{F_n}(y)) \\&= E(\hat{F_n}(x) \hat{F_n}(y)) - F(x)F(y)
\end{align}
$$
Then we have
$$
E(\hat{F_n}(x) \hat{F_n}(y)) = \frac{1}{n} F(\min\{x, y\}) + \left( 1 - \frac{1}{n}\right) F(x)F(y)
$$

Assume $x < y$
$$
\begin{align}
\\Cov(\hat{F_n}(x),\hat{F_n}(y)) & = E(\hat{F_n}(x) \hat{F_n}(y)) - E(\hat{F_n}(x))E(\hat{F_n}(y)) \\&= E(\hat{F_n}(x) \hat{F_n}(y)) - F(x)F(y)\\&=

\frac{1}{n} F(\min\{x, y\}) + \left( 1 - \frac{1}{n}\right) F(x)F(y)-F(x)F(y)\\&=
 \frac{F(x)(1 - F(y))}{n}
\end{align}
$$



